Fluid-mechanical erosion creates anisotropic porous media

### 2022-05-23 docs/PhysicsPaper/StokesErosion.tex
NM

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% TITLE AUTHORS ABSTRACT
\begin{document}
\title{Fluid-mechanical erosion creates anisotropic porous media}
%\title{Fluid-mechanical erosion generates anisotropy in porous media}
%\title{Erosion leads to anisotropy in a porous medium}
%\title{The development of anisotropy in an eroding porous medium}

@@

\nick{Perhaps you can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}

@@

There are two possible explanations for how erosion creates anisotropy in the microstructure. First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains. Second, by removing material in a non-uniform way, could preferentially disintegrate certain bodies before others, leaving an overall configuration that exhibits anisotropy on the large scale. We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively. As an extreme example, a tightly spaced row of circular bodies would exhibit configurational anisotropy but no shape anisotropy. Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.

>>>>

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% TITLE AUTHORS ABSTRACT
\begin{document}
\title{Fluid-mechanical erosion creates anisotropic porous media}

% Maybe HOW fluid-mechanical erosion creates anisotropic porous media.
%\title{Fluid-mechanical erosion generates anisotropy in porous media}
%\title{Erosion leads to anisotropy in a porous medium}
%\title{The development of anisotropy in an eroding porous medium}

@@

\nick{Perhaps we can combine the real BIE and Cauchy representation into one section to condense it and to make the complex analysis take more center stage.}

@@

There are two possible explanations for how erosion creates anisotropy in the microstructure. First, the shear stresses could carve each individual body into a more slender form, thus creating anisotropy at the level of individual grains. Second, by removing material in a non-uniform way, could preferentially disintegrate certain bodies before others, leaving an overall configuration that exhibits anisotropy on the large scale. We will refer to these two possible mechanisms as {\em shape} anisotropy and {\em configurational} anisotropy respectively. As an extreme example, a tightly-packed horizontal row of circular bodies would exhibit configurational anisotropy but no shape anisotropy. Meanwhile, an array of highly eccentric ellipses, all oriented horizontally but positioned randomly, would exhibit high shape anisotropy and low configurational anisotropy.
